
\section{lua-\LaTeX{} Font Options (you compiled with lualatex)}

If you compile your document with LuaLaTeX, you can easily change the font using the \texttt{fontspec} package.\\

This class implements an automated engine-check, considering if you compile with luaLaTeX or pdfLaTeX.
If needed, the \texttt{fontspec} package is included automatically.\\

To compile your document with luaLaTeX instead of pdfLaTeX, you need to implement an additional recipe in your \texttt{settings.json} (see~\ref{settingsjson}).\\

For ease of use, a macro:

\textcolor{blue}{\textbackslash fontX\{FontName\}\{Text\}} is provided to switch fonts. 
Make sure you have these fonts installed on your system to see the effect.\\

Below are some examples of different fonts.\\

\begin{itemize}[noitemsep]
    \item \fontX{Arial}{\textbf{Arial:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{inter}{\textbf{Inter:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{consolas}{\textbf{Consolas:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{comic sans ms}{\textbf{Comic Sans:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{agency fb}{\textbf{Agency FB:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{exo}{\textbf{Exo:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{exo 2}{\textbf{Exo 2:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{calibri}{\textbf{Calibri:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{tahoma}{\textbf{Tahoma:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{bookantiqua}{\textbf{Book Antiqua:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{garamond}{\textbf{Garamond:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{timesnewroman}{\textbf{Times New Roman:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \fontX{georgia}{\textbf{Georgia:}\qquad The quick brown fox jumps over the lazy dog.}
    \item \textbf{Default:} \qquad The quick brown fox jumps over the lazy dog
\end{itemize}
